Non-word repetition in Yélî Dnye

### 2022-02-21 manuscript.Rmd
version for final proofing

```{r tablength, results = "asis"}
length.tab=NULL
for(myvar in c("Word","NLD")){
  length.tab=cbind(length.tab,
              paste0(round(aggregate(by_length[,myvar],by=list(by_length$Length),mean)$x),
              " (",round(aggregate(by_length[,myvar],by=list(by_length$Length),sd)$x),")"))
}
rownames(length.tab)<-paste(c(1:4),"syll")
colnames(length.tab)<-c("Word","NLD")
kable(length.tab,"latex", booktabs = T,caption="NWR means (and standard deviations) measured in whole-word scores and normalized Levenshtein Distance (NLD), separately for the four stimuli lengths.")
```

>>>>

```{r tablength, results = "asis"}
length.tab=NULL
for(myvar in c("Word","NLD")){
  length.tab=cbind(length.tab,
              paste0(round(aggregate(by_length[,myvar],by=list(by_length$Length),mean)$x),
              " (",round(aggregate(by_length[,myvar],by=list(by_length$Length),sd)$x),")"))
}
rownames(length.tab)<-paste(c(1:4),"syll")
colnames(length.tab)<-c("Word","NLD")
kable(length.tab,"latex", booktabs = T,caption="NWR means (and standard deviations) measured in whole-word scores and normalized Levenshtein Distance (NLD), separately for the four stimuli lengths.")

write.csv(length.tab,"tab4.csv")
```
